quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-10-15 paper-quollr.Rmd
Remove some outputs

```{r, echo=TRUE}
scurve_umap_obj <- gen_scaled_data(nldr_data = scurve_umap)

scurve_umap_obj
```

@@

```{r, echo=TRUE}
find_low_dens_hex(
  model_2d = df_bin_centroids, 
  b1 = 25, 
  md_thresh = 0.05
)
```

@@

```{r, echo=TRUE}
model_error <- augment(
  x = scurve_model_obj,
  highd_data = scurve
  )

head(model_error, 5)
```

>>>>

```{r, echo=TRUE}
scurve_umap_obj <- gen_scaled_data(nldr_data = scurve_umap)
```

@@

```{r, echo=TRUE}
low_density_hex <- find_low_dens_hex(
  model_2d = df_bin_centroids, 
  b1 = 25, 
  md_thresh = 0.05
)
```

@@

```{r, echo=TRUE}
model_error <- augment(
  x = scurve_model_obj,
  highd_data = scurve
  )
```

### 2025-10-15 paper-quollr.tex
Remove some outputs

\begin{verbatim}
scurve_umap_obj <- gen_scaled_data(nldr_data = scurve_umap)

scurve_umap_obj
\end{verbatim}

\begin{verbatim}
> $scaled_nldr
> # A tibble: 1,000 x 3
>     emb1  emb2    ID
>    <dbl> <dbl> <int>
>  1 0.300 0.985     1
>  2 0.721 0.688     2
>  3 0.722 0.542     3
>  4 0.196 1.01      4
>  5 0.240 1.06      5
>  6 0.621 1.19      6
>  7 0.159 0.160     7
>  8 0.979 0.661     8
>  9 0.870 0.963     9
> 10 0.885 0.501    10
> # i 990 more rows
> 
> $lim1
> [1] -8.320406  8.522628
> 
> $lim2
> [1] -11.732897   9.679631
\end{verbatim}

@@

\begin{verbatim}
find_low_dens_hex(
  model_2d = df_bin_centroids, 
  b1 = 25, 
  md_thresh = 0.05
)
\end{verbatim}

\begin{verbatim}
>   [1]  82  83 106 107 108 109 131 132 133 134 135 156 157 158 159 160 161 162
>  [19] 179 180 181 183 184 185 186 188 189 190 204 205 206 207 208 209 210 211
>  [37] 214 215 216 217 228 229 230 231 232 233 234 235 236 238 239 240 241 242
>  [55] 254 255 256 257 258 259 260 261 263 264 265 266 267 268 269 279 280 281
>  [73] 283 284 285 286 287 288 289 290 293 294 305 306 307 308 309 310 311 312
>  [91] 313 314 315 316 317 318 319 320 321 331 332 333 334 335 336 337 339 340
> [109] 341 342 344 345 346 358 359 360 361 362 363 364 365 366 367 369 370 371
> [127] 372 386 387 388 389 390 391 392 393 394 395 396 414 415 416 417 418 419
> [145] 420 421 422 440 441 442 443 444 445 446 447 467 468 469 470 471 472 473
> [163] 491 492 493 494 495 496 497 498 518 519 520 522 523 541 542 543 544 545
> [181] 546 547 548 554 558 560 566 567 568 569 570 571 572 573 578 579 580 581
> [199] 582 583 584 585 586 587 588 590 591 592 593 594 595 596 597 598 603 604
> [217] 605 606 607 608 609 610 611 612 613 614 615 616 617 618 619 620 621 622
> [235] 623 629 630 631 633 634 635 636 637 638 639 640 641 642 643 644 645 646
> [253] 647 653 654 655 656 657 658 659 660 661 662 663 664 665 666 667 668 669
> [271] 670 671 672 678 679 680 681 682 683 684 685 686 687 688 689 690 691 692
> [289] 693 694 695 696 703 704 705 706 707 708 709 710 711 712 713 714 716 717
> [307] 718 719 720 721 728 729 730 731 732 733 734 736 737 738 739 741 742 743
> [325] 744 754 755 756 757 758 759 760 761 762 763 764 765 766 767 768 779 781
> [343] 782 783 784 785 786 787 788 789 790 791 792 807 808 809 810 811 812 813
> [361] 814 837
\end{verbatim}

@@

\begin{verbatim}
model_error <- augment(
  x = scurve_model_obj,
  highd_data = scurve
  )

head(model_error, 5)
\end{verbatim}

\begin{verbatim}
> # A tibble: 5 x 32
>      ID      x1    x2       x3       x4       x5      x6       x7 pred_h
>   <int>   <dbl> <dbl>    <dbl>    <dbl>    <dbl>   <dbl>    <dbl>  <int>
> 1     1 -0.120  0.819 -1.99     0.0114   0.00351  0.0334  0.00638    427
> 2     2 -0.0492 0.166  0.00121  0.0115  -0.0166  -0.0297  0.00509    287
> 3     3 -0.774  0.651  0.367   -0.0172   0.00600  0.0211  0.00303    226
> 4     4 -0.606  0.952 -1.80     0.0157  -0.00978 -0.0590 -0.00754    446
> 5     5 -0.478  1.10  -1.88    -0.00423  0.00495 -0.0482 -0.00982    468
> # i 23 more variables: model_high_d_x1 <dbl>, model_high_d_x2 <dbl>,
> #   model_high_d_x3 <dbl>, model_high_d_x4 <dbl>, model_high_d_x5 <dbl>,
> #   model_high_d_x6 <dbl>, model_high_d_x7 <dbl>, error_square_x1 <dbl>,
> #   error_square_x2 <dbl>, error_square_x3 <dbl>, error_square_x4 <dbl>,
> #   error_square_x5 <dbl>, error_square_x6 <dbl>, error_square_x7 <dbl>,
> #   row_wise_total_error <dbl>, abs_error_x1 <dbl>, abs_error_x2 <dbl>,
> #   abs_error_x3 <dbl>, abs_error_x4 <dbl>, abs_error_x5 <dbl>, ...
\end{verbatim}

>>>>

\begin{verbatim}
scurve_umap_obj <- gen_scaled_data(nldr_data = scurve_umap)
\end{verbatim}

@@

\begin{verbatim}
low_density_hex <- find_low_dens_hex(
  model_2d = df_bin_centroids, 
  b1 = 25, 
  md_thresh = 0.05
)
\end{verbatim}

@@

\begin{verbatim}
model_error <- augment(
  x = scurve_model_obj,
  highd_data = scurve
  )
\end{verbatim}
